Growth model analysis

### 2017-12-15 manuscriptAnalysis/MS_Analysis.Rmd
spp-specific model runs working

ggsave('figures/rawCount.png')
```

>>>>

ggsave('figures/rawCount.png')

tmp <- d %>% distinct(season,year,sampleNumber)
allFishBySpecies <- left_join(allFishBySpecies,tmp)
allFish <- left_join(allFish,tmp)

ggplot(allFishBySpecies, aes(sampleNumber,nAllFishBySpecies)) +
  geom_point(aes(color = speciesGG)) +
  geom_line(aes(color = speciesGG)) +
  geom_line( data = allFish, aes(sampleNumber,nAllFish) ) +
  theme_publication() +
  labs( x = "SampleNumber", y = "Count" ) +
  facet_wrap(  ~riverOrderedGG )#, scales = "free_y" )
